The Cluster Difference Imaging Photometric Survey (CDIPS). I. Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-07-01 paper/ms.tex
add age figure to paper

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{target_star_cumulative_counts.png}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    {\bf Cumulative number of target stars as
    a function of Gaia $Rp$-band magnitude.}  The selected stars are
    either candidate members of clusters, or else have other youth
    indicators (see \S~\ref{sec:starselection}). We only consider
    stars with $G_{\rm Rp} < 16$.
	\label{fig:cdips_targets}
	}
\end{figure}

@@

To assign unique cluster names, we adopted the name matched against
\citet{Kharchenko_et_al_2013} whenever possible, following the
procedure described in Appendix~\ref{appendix:uniquenames}.  For
moving groups not identified in \citet{Kharchenko_et_al_2013}, we used
the constellation-based naming convention from
\citet{gagne_banyan_XI_2018}.  Otherwise, we used the name reported by
the original catalog claiming membership.  This process reduced 16,425
name permutations down to 3,216 unique cluster names.  Though we have
made every effort to avoid duplicates, a small number may remain, so we
advise inspection of the \texttt{cluster} column
as well as the references given in the
\texttt{reference} column rather than using the
\texttt{unique\_cluster\_name} column to analyze individual objects
of interest.  Nonetheless, 87.7\% of the $\sim$million unique target
stars are matched to clusters within \citet{Kharchenko_et_al_2013},
and 88.8\% are assigned a cluster name.  The remainder are mostly the
young stars from \citet{zari_3d_2018}.

The resulting CDIPS target star list is given in Table~N.
The distribution of target star brightnesses is shown in
Figure~\ref{fig:cdips_targets}.

>>>>

\begin{figure}[t]
	\begin{center}
		\leavevmode
    %\includegraphics[width=0.45\textwidth]{target_star_cumulative_counts.png}
    \gridline{\fig{target_star_cumulative_counts.png}{0.45\textwidth}{}}
    \vspace{-0.8cm}
    \gridline{\fig{target_star_hist_logt.png}{0.45\textwidth}{}}
	\end{center}
	\vspace{-0.8cm}
	\caption{
    {\it Top.} Cumulative number of target stars as
    a function of Gaia $Rp$-band magnitude.  The selected stars are
    either candidate members of clusters, or else have other youth
    indicators (see \S~\ref{sec:starselection}). We only consider
    stars with $G_{\rm Rp} < 16$.
    {\it Bottom.} Histogram of target star ages, for the subset of
    stars with ages matched against \citet{Kharchenko_et_al_2013}.
	\label{fig:cdips_targets}
	}
\end{figure}

@@

To assign unique cluster names, we adopted the name matched against
\citet{Kharchenko_et_al_2013} whenever possible, following the
procedure described in Appendix~\ref{appendix:uniquenames}.  For
moving groups not identified in \citet{Kharchenko_et_al_2013}, we used
the constellation-based naming convention from
\citet{gagne_banyan_XI_2018}.  Otherwise, we used the name reported by
the original catalog claiming membership.  This process reduced 16,425
name permutations down to 3,216 unique cluster names.  Though we have
made every effort to avoid duplicates, a small number may remain, so we
advise inspection of the \texttt{cluster} column
as well as the references given in the
\texttt{reference} column rather than using the
\texttt{unique\_cluster\_name} column to analyze individual objects
of interest.  Nonetheless, 87.7\% of the $\sim$million unique target
stars are matched to clusters within \citet{Kharchenko_et_al_2013},
and 88.8\% are assigned a cluster name.  The remainder are mostly the
young stars from \citet{zari_3d_2018}.
Ages and their uncertainties are then merged against the 
parameters reported by \citet{Kharchenko_et_al_2013}.

The resulting CDIPS target star list is given in Table~N.
The cumulative distribution of target star brightnesses, as well as a
histogram of the ages, is shown in Figure~\ref{fig:cdips_targets}.
Relative to field stars, our target star sample is young, with a
typical age of 100$\,$Myr.
